Characterization of gaps in directly bonded Si compound optics

### 2014-04-21 AO_bondedSi.tex
add in two theory figures, make some edits in the text for those figures

@@

\subsection{The air cavity is a low Finesse Fabry-P\`{e}rot etalon}

The air cavity is a low-Finesse Fabry-P\`{e}rot etalon\cite{2007fuph.book.....S}.  Note that we imprecisely refer to the gap as an air gap, though in principle the gap has an unknown mixture of gases for example water vapor, or other vapors that were outgassed from reactions catalyzed by hydrocarbons.  The transmission through a Fabry-P\`{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We assume transmission is at normal incidence, the refractive index of the gap is 1.0, and the material is at room temperature.  Si is negligibly absorbing longward of $\lambda$ = 1150 nm, which we verified with comparison of Si reference samples of different thicknesses.  We compute the reflectivity for an Si$-$air interface, which is a modest function of wavelength through the refractive index of Silicon, $n(\lambda, T)$ \cite{2006SPIE.6273E..77F}, as shown in Figure \ref{figSiIndexFinesse}.  In the equations ahead we drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ for clarity.  The computation is simply Fresnel's law at normal incidence:

$$
T_{DSP} = \frac{2n}{1+n^2}
$$

which has an average value of about 53\%.  Note that this transmission is above a na\"ive value of $T_{DSP}=(1-R^2)$, which does not take into account multiple incoherent reflections, and is therefore an underestimate.  If the Si wafer path thickness is less than the coherence length for the given spectral bandwidth, then the multiple reflections would interfere coherently, and the Si wafer would behave as a Fabry-P\`erot etalon.  This scenario is beyond the scope of this paper, since we are primarily interested in thick substrates with small gaps in between the interfaces.
%We work out this behavior in the Appendix and show that in the limit $l>> \lambda^2 / \delta \lambda $ the spectral transmission tends to equation X.

Now consider a pair of bonded Si pucks with a gap thickness $d$. We derive the absolute transmission bonded Si wafers with a gap in Equation \ref{eqn:Tetalon} in the Appendix.  We normalize the absolute transmission by the transmission with no gap to isolate the effect of the gap.  We call this normalized transmission the etalon transmission $T_{e}$, since it isolates the effect of the etalon on the transmission.

It is clear that in the limit $\lim_{d \rightarrow 0}$, the etalon approaches 100\% transmission.  In the next section we compare measurements to by-eye fits of this equation.

@@

\subsection{Constructing the predicted transmission}
We constructed the predicted transmission in the following way.  If IR imaging was unavailable, our optimistic prior belief was simply that the bond should be perfect and indistinguishable from a solitary DSP Si wafer, (i.e. 100\% relative transmission).  For the cases where we had bored gaps of known dimension and fill factors we could predict the transmission with the Fabry-Perot machinery described in section \ref{secTheory}.  Specifically we apply Equation \ref{eqFP}.  For non-unit fill factor, we simply average 100\% transmission with the predicted gap transmission, weighted by the estimated fill factor listed in Table \ref{tabPatternFills}.  No attempt was made to verify the delivered fill factor, but since high precision lithographic processes were employed, we assume the delivered fill factor is equal to the designed fill factor with no uncertainty.  The depth of the meshes has an associated uncertainty listed in \ref{tabbondexper}.  We incorporated the uncertainty in the mesh depth in the following way.  We computed the transmission curve for the 1$\sigma$ lower and upper bounds, and plot a filled band marked as the prediction band.  The uncertainties in the mesh depths were low enough that the band spread includes all intermediate lines of predicted transmission between plus and minus 1$\sigma$.  In cases where the IR imaging was unavailable the mesh position was only coarsely known, so our prediction band had to incorporate our uncertainty about whether or not our measurement beam was on or off or overlapping the mesh border.  If the beam was off the mesh we assumed 100\% relative transmission, so we simply set the lower bound of the predicted transmission to the equivalent of a zero gap.

>>>>

\subsection{The Si-Si interface gap is a low Finesse Fabry-P\`{e}rot etalon}

The Si-Si interface gap is a low-Finesse Fabry-P\`{e}rot etalon\cite{2007fuph.book.....S}.  The transmission through a Fabry-P\`{e}rot depends on the wavelength of light, the reflectivity of the etalon sidewalls, and the size of the gap.  We assume transmission is at normal incidence, the refractive index of the gap is 1.0, and the material is at room temperature.  Si is negligibly absorbing longward of $\lambda$ = 1150 nm, which we verified with comparison of Si reference samples of different thicknesses.  We compute the reflectivity for an Si$-$air interface, which is a modest function of wavelength through the refractive index of Silicon, $n(\lambda, T)$ \cite{2006SPIE.6273E..77F}, as shown in Figure \ref{figSiIndexFinesse}.  In the equations ahead we drop the subscripts on the refractive index $n(\lambda, T) \rightarrow n$ for clarity.  The computation is simply Fresnel's law at normal incidence:

$$
T_{DSP} = \frac{2n}{1+n^2} \label{eqnAbsDSPtrans}
$$

which has an average value of about 53\%.  Note that this transmission is above a na\"ive value of $T_{DSP}=(1-R^2)$, which does not take into account multiple incoherent reflections, and is therefore an underestimate.  Figure \ref{figAbsoluteTrans} shows a plot of Equation \ref{eqnAbsDSPtrans} in the wavelength range 1200$-2500$ nm.  If the Si wafer path thickness is less than the coherence length for the given spectral bandwidth, then the multiple reflections would interfere coherently, and the Si wafer would behave as a Fabry-P\`erot etalon.  This scenario is beyond the scope of this paper, since we are primarily interested in thick substrates with small gaps in between the interfaces.%We work out this behavior in the Appendix and show that in the limit $l>> \lambda^2 / \delta \lambda $ the spectral transmission tends to equation X.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.45\columnwidth]{figs/20140421_absolute.pdf}}
\caption{Modeled absolute transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figAbsoluteTrans}.  The absolute transmission through Si depends on the Si refractive index, which depends on wavelength. }
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.45\columnwidth]{figs/20140421_absoluteB.pdf}}
\caption{Modeled etalon transmission through a silicon substrate with no gap (top black solid curve), and small gaps of axial extent 20 nm (red dashed curve) and 35 nm (cyan triple-dot dashed curve)\label{figEtalonRelTrans}.  The curves are examples from a family defined in Equation \ref{eqFP}.   The limit of no gap is 100\% transmissive, compared to a DSP reference.  A 35 nm gap degrades the transmission over a DSP reference by 4\% at 1200 nm.}
\end{figure}

Now consider a pair of bonded Si pucks with a gap thickness $d$. We derive the absolute transmission of bonded Si substrates with a gap in Equation \ref{eqn:Tetalon} in the Appendix.  We normalize the absolute transmission by the transmission with no gap to isolate the effect of the gap.  We call this normalized transmission the etalon transmission $T_{e}$, since it isolates the effect of the etalon on the transmission.

It is clear that in the limit $\lim_{d \rightarrow 0}$, the etalon approaches 100\% transmission.  Figure \ref{figEtalonRelTrans} shows a plot of Equation \ref{eqFP} for gap sizes, $d$, of 20 nm and 35 nm.  In the next section we compare measurements to by-eye fits of this equation.

@@

@@

\subsection{Constructing the predicted transmission}
We constructed the predicted transmission in the following way.  If IR imaging was unavailable, our optimistic prior belief was simply that the bond should be perfect and indistinguishable from a solitary DSP Si wafer, (i.e. 100\% relative transmission).  For the cases where we had bored gaps of known dimension and fill factors we could predict the transmission with the Fabry-Perot machinery described in section \ref{secTheory}.  Specifically we apply Equation \ref{eqFP}.  For non-unit fill factor, we simply average 100\% transmission with the predicted gap transmission, weighted by the estimated fill factor listed in Table \ref{tabPatternFills}.  No attempt was made to verify the delivered fill factor, but since high precision lithographic processes were employed, we assume the delivered fill factor is equal to the designed fill factor with no uncertainty.  The depth of the meshes has an associated uncertainty listed in Table \ref{tabbondexper}.  We incorporated the uncertainty in the mesh depth in the following way.  We computed the transmission curve for the 1$\sigma$ lower and upper bounds, and plot a filled band marked as the prediction band.  The uncertainties in the mesh depths were low enough that the band spread includes all intermediate lines of predicted transmission between plus and minus 1$\sigma$.  In cases where the IR imaging was unavailable the mesh position was only coarsely known, so our prediction band had to incorporate our uncertainty about whether or not our measurement beam was on or off or overlapping the mesh border.  If the beam was off the mesh we assumed 100\% relative transmission, so we simply set the lower bound of the predicted transmission to the equivalent of a zero gap.
